Missing data: Current practice in football research and recommendations for

### 2020-09-11 paper/paper.Rmd
make changes to the simulated data set and missing data plots (a,b,c).

---
title: 'Missing data: Current practice in football research and recommendations for
  improvement'
bibliography: references.bib
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
---

@@

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
```

@@

(Figure \@ref(fig:missing-overview)) give an overall sense of the extent of missing and complete data. 
The simualted data set contains ... **Add short description (1-2 sentences) here of the simulated data set**

@@

# Aim of this section:
# Simulate data from a real data set, insert missing
# 'Study aim': predicting hamstring strain injury, using number of sprints and sprint distance as x-variables
# We need to add a sentence in the paper talking about this
# I'm stuck at the momement how to simulate the occurance of an injury (0,1), but with only low incidence of 1's in the dataset
# I'm also stuck how to simulate the number of sprints, but between say 50 and 200 sprints

# Generate the x-variables
# d <- get_afltables_stats(start_date = "2020-01-01", end_date = "2020-09-04")
# 
# data <-
#   d %>% select(
#     ID,
#     Round,
#     First.name,
#     Surname
#     )

@@

# # Simulate number of sprints per game
# Observations = nrow(data)
# sprints <- sample.int(100, # numbers of sprints between 1 and 100
#            nrow(data),
#            replace = T) # observations
# 
# # Simulate incidence of hamstring strain injuries
# # sample.int(100, # numbers of sprints between 1 and 100
# #            nrow(data),
# #            replace = T) # observations
# 
# data <- merge(data, sprints)
# 
# # Impute missing values
# data <- ampute(data = df[,10:43])
# data <- df_first_try$amp
# 
# 
# 
# # Put the dataset together
# # Impute missing values
# data <- ampute(data = df[,10:43])
# data <- data$amp

```{r missing-overview, fig.cap = "Overviews of missing values in airquality data. Panel A shows... Panel B shows ... Panel C shows ... (simulate data from football study, provide write up in the supplementary materials)", fig.height = 10}

aq_vis_miss <- vis_miss(airquality)

aq_upset <- gg_miss_upset(airquality)

aq_fct <- gg_miss_fct(airquality, Month)

aq_miss_var <- gg_miss_var(airquality) + labs(title = "A")
aq_miss_case <- gg_miss_case(airquality) + labs(title = "B")
aq_vis_miss <- vis_miss(airquality) + labs(title = "C")

>>>>

---
title: 'Missing data: Current practice in football research and recommendations for
  improvement'
bibliography: references.bib
output:
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
---

@@

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
library(truncnorm)
library(janitor)
```

@@

(Figure \@ref(fig:missing-overview)) give an overall sense of the extent of missing and complete data, in an simulated injury dataset, from Australian Rules football matches, played in August 2020. The dataset contains observed player id, team, and match venue data, in addition to simulated data on injury incidence, and number of sprints per match, and total sprint distance per match. Researchers might be interested in investigating the relationship between number of sprints and total sprint distance with incidence of injury. **should we include this last sentence?**

@@

# Aim of this section:
# Simulate data from a real data set, insert missing
# 'Study aim': predicting hamstring strain injury, using number of sprints and sprint distance as x-variables

# Simulate dataset
d <- get_afltables_stats(start_date = "2020-08-01", end_date = "2020-09-01")

data_afl <- d %>% select(ID, Round, Playing.for, Venue)

# Simulate injury and sprint variables
injury <- rbinom(n = nrow(d), 1, prob = 0.1)
sprints <- rpois(n = nrow(d), lambda = 100)
sprint_distance <- truncnorm::rtruncnorm(n = nrow(d), a = 0, b = Inf, mean = 2000, sd = 500) # Check if this is reasonable (mean 2 km per game)

data <- cbind(injury, sprints, sprint_distance)

# Impute missing values
data_impute <- ampute(data = data[,1:3])
data_with_missing <- data_impute$amp

# Put the dataset together
data_plot <- cbind(data_afl, data_with_missing)

# Clean variable names
data_plot <- data_plot %>% clean_names() %>% rename(team = playing_for)

@@

```{r missing-overview, fig.cap = "Overviews of missing values in simulated injury data in Australian Football matches for August, 2020. Panel A shows... Panel B shows ... Panel C shows ...", fig.height = 10}

aq_vis_miss <- vis_miss(data_plot)

aq_upset <- gg_miss_upset(data_plot)

aq_fct <- gg_miss_fct(data_plot, team)

aq_miss_var <- gg_miss_var(data_plot) + labs(title = "A")
aq_miss_case <- gg_miss_case(data_plot) + labs(title = "B")
aq_vis_miss <- vis_miss(data_plot) + labs(title = "C")
